A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-22 colt-21/cvx-flats-before-cuts.tex
Going to start trimming things, so separated file with old statements.

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let flat $F\subseteq \P$ be a $d$-representation containing some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item $p \in \relint{F}$; 
  	\item $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
  	\item Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
  \end{enumerate}
\end{lemma}
\begin{proof}

	(1.)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, we have $q_\alpha \in F$.
	Therefore, $p \in \relint{F}$. \jessie{Feels insufficient}

@@

	(2.)
	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-representation.)

@@

	(3.)
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	First, observe $v \in F_p \iff p + v \in F$.
	As $p \in \relint{\P}$, by part (1.), we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$.

	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex. %, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
	The result follows by applying the definition of the subspace of feasible directions.	
\end{proof}

>>>>

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
%Moreover, $\ker(W) = \{p \in \spn(\P): Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
  	\item[(iii)] Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
  \end{enumerate}
\end{lemma}
\begin{proof}

	(i)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, we claim $q_\alpha \in F$.
	Observe $p \in F \implies \E_p V(Y) = \vec 0$, and $q \in F \implies \E_q V(Y) = \vec 0$.
	By linearity of expectation, we then have $\E_{q_\alpha} V(Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
	This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

@@

	(ii)
	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-representation.)

@@

	(iii)
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	By (i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
	Consider $v \in F_p$.
	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and by construction of $F$ as the kernel space of a subgradient of a convex loss\jessiet{We need the loss setup here and the loss to be convex... makes me think this last part should be pulled out into its own statement.}
	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}
